---
title: "ltertools Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ltertools Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-mechanics, include = F}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

```{r pre-setup, echo = FALSE, message = FALSE}
# devtools::install_github("lter/ltertools")
```

## Overview

The `ltertools` package 

The goal of `ltertools` is to centralize the R functions created by members of the Long Term Ecological Research (LTER) community. Many of these functions likely have broad relevance that expands beyond the context of their creation and this package is an attempt to share those tools and limit the amount of "re-inventing the wheel" that we each do in our own silos.

The conceptual theme of functions in `ltertools` is necessarily broad given the scope of the community we aim to serve. That said, the identity of this package will likely become more clear as we accrue contributed functions. This vignette describes the main functions of `ltertools` as they currently exist.

```{r setup}
# devtools::install_github("lter/ltertools")
library(ltertools)
```

### Harmonization

`begin_key`


`harmonize`


### Wrangling

`read`



`cv`


`convert_temp`



### LTER Information

The LTER Network is composed of many separate sites. While all of these sites are "long term" they do vary slightly in when they were created. For those interested in knowing the temporal coverage of data from a particular site or group of sites, `site_timeline` can prove a helpful function. This function creates a `ggplot2` timeline where sites are on the vertical axis and years are on the horizontal. Lines are colored based on the habitat of the site and there is support for a user-defined set of hexadecimal colors though by default an internal palette is used.

Sites can be specified by their three letter site code or all sites in a particular habitat can be included.
```{r site-timeline-1, fig.align = 'center', fig.height = 3, fig.width = 7}
# Check the timeline for all grassland or forest LTER sites
ltertools::site_timeline(habitats = c("grassland", "forest"))
```

Running the function without specifying site codes or habitat types will result in a timeline of all active LTER sites.
```{r site-timeline-2, fig.align = 'center', fig.height = 4, fig.width = 7}
# Check the timeline for all LTER sites
ltertools::site_timeline()
```
